Anomalous waves triggered by abrupt depth changes: experiments and truncated KdV theory

### 2019-10-12 paper2_JNLS/paper.tex
NM

	Next, Fig.~\ref{transfig}(b) shows the skewness of the incoming (green) and outgoing (blue) wave fields, as they depend on the incoming inverse temperature $\thup$ for the case $(\Lambda, \lamfac) = (16, 8)$. In line with experimental observations, the incoming skewness is small, while the outgoing wave skewness is much higher. Specifically, to capture the experimentally observed peak skewness range of 0.6-0.9 seen for the larger amplitudes in Fig.~\ref{ExpSpatialStats}(b), requires selecting $\thup$ in the range 10--20.

@@

	We now aim to compare the wave statistics measured in experiments against those that emerge from the TKdV theory. Throughout, we will focus on the representative set of experiments detailed in Table \ref{paramtable}. In these experiments, the peak downstream skewness was measured to be 0.83. We can then use Fig.~\ref{transfig}(c) as a guide to select the appropriate upstream inverse temperature $\thup$. With $(\Lambda, \lamfac) = (16, 8)$ fixed, the figure indicates a value of $\thup = 17$ achieves the desired outgoing skewness. We thus run the deterministic TKdV simulations with model parameters $\Lambda = 16$, $\lamfac = 8$, $\thup = 17$ and with $\epsup$, $\delup$, and $\dratdn$ set to the representative values in Table \ref{paramtable}. We run the simulations to a sufficiently long dimensionless time of $t_{f} = 10$, with $dt = 5 \times 10^{-4}$ and with $10^3$ trajectories sampled from the upstream Gibbs measure $\Gup$.

@@

\vsp{10}
%----------------------------------------------------------%
% Direct numerical simulations
%----------------------------------------------------------%
\section{Direct numerical simulations}

\section{Sampling Algorithms}
%\subsection{Naive acceptance-rejection algorithm}
%\subsection{Markov-chain Monte Carlo}
%\subsection{Improved acceptance-rejection algorithm}

%----------------------------------------------------------%
% Comparison with experiments
%----------------------------------------------------------%
\section{Comparison with experiments}

>>>>

	Next, Fig.~\ref{transfig}(b) shows the skewness of the incoming (green) and outgoing (blue) wave fields, as they depend on the incoming inverse temperature $\thup$ for the case $(\Lambda, \lamfac) = (16, 8)$. In line with experimental observations, the incoming skewness is small, while the outgoing wave skewness is much higher. Specifically, to capture the experimentally observed peak skewness range of 0.6-0.9 seen for the larger amplitudes in Fig.~\ref{ExpSpatialStats}(b), requires selecting $\thup$ in the range 10--20 (?).

@@

	We now aim to compare the wave statistics measured in experiments against those that emerge from the TKdV theory. Throughout, we will focus on the representative set of experiments detailed in Table \ref{paramtable}, in which the peak downstream skewness was measured to be 0.83. 
%We can then use Fig.~\ref{transfig}(c) as a guide to select the appropriate upstream inverse temperature $\thup$. With $(\Lambda, \lamfac) = (16, 8)$ fixed, the figure indicates a value of $\thup = 17$ achieves the desired outgoing skewness. We thus run the deterministic TKdV simulations with model parameters $\Lambda = 16$, $\lamfac = 8$, $\thup = 17$ and with $\epsup$, $\delup$, and $\dratdn$ set to the representative values in Table \ref{paramtable}. 
%
With $(\Lambda, \lamfac) = (16, 8)$ fixed, Fig.~\ref{transfig}(c) indicates $\thup = 20$ as a reasonable value to attain the desired skewness. We thus run the deterministic TKdV simulations these model parameters and with $\epsup$, $\delup$, and $\dratdn$ set to the representative values in Table \ref{paramtable}. We run the simulations to a sufficiently long dimensionless time of $t_{f} = 10$, with $dt = 5 \times 10^{-4}$ and with $10^3$ trajectories sampled from the upstream Gibbs measure $\Gup$.

@@
